Some Correlations were Found between the efforts made by the Staff of Toronto's Central Intake Line and Toronto's Homeless Death Counts

### 2024-01-23 outputs/paper/paper.qmd
Changed geom_jitter to goem_point, may change later

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_jitter() + geom_smooth() + 
  geom_line(aes(x = Month, y = Calls_Coded_month/1000), color = "red") +
  labs(
    title = "Correlation between number of Calls Coded and Homeless Death Count",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

@@

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_jitter() + geom_smooth() + 
  geom_line(aes(x = Month, y = Referral_to_Shelter_month/100), color = "purple") +
  labs(
    title = "Correlation between of Callers Referred to Shelter & Homeless Death",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

@@

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_jitter() + geom_smooth() + 
  geom_line(aes(x = Month, y = Information_Homelessness_and_Prevention_month/100), color = "darkgreen") +
  labs(
    title = "Correlation between Callers given Info on Homelessness Prevention and Homeless Death",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

>>>>

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_point() + geom_smooth() + 
  geom_line(aes(x = Month, y = Calls_Coded_month/1000), color = "red") +
  labs(
    title = "Correlation between number of Calls Coded and Homeless Death Count",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

@@

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_point() + geom_smooth() + 
  geom_line(aes(x = Month, y = Referral_to_Shelter_month/100), color = "purple") +
  labs(
    title = "Correlation between of Callers Referred to Shelter & Homeless Death",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```

@@

combined_data|> ggplot(mapping = aes(x = Month, y = Death_Count)) + 
  geom_point() + geom_smooth() + 
  geom_line(aes(x = Month, y = Information_Homelessness_and_Prevention_month/100), color = "darkgreen") +
  labs(
    title = "Correlation between Callers given Info on Homelessness Prevention and Homeless Death",
    x = "Time (in Month)",
    y = "Count"
  )
#still need to add a legend or label, but I haven't yep figured out how
```
